Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-30 papers/LREC2020/conclusion.tex
lrec submission revised until conclusion; 3 lines overspill

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
Our data suggests that this is not always the case and can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
% (as in the case where they label objects as the background, like \word{grass} for \word{dog}).

@@

Our current data clearly supports the prediction in theoretical research on object naming and categorization that there will in general be a preferred name for a given visually presented object.
It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.

>>>>

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.

@@

With respect to naming variation, our current data clearly supports the prediction in theoretical research on object naming that there will in general be a preferred (entry-level) name for a given visually presented object.
It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.
